An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-01 mixedwindow.tex

\section{Introduction} This paper proposes an out-of-sample (\oos)
test statistic that is asymptotically normal with mean zero even when
the models studied are nested.
\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

\section{Monte Carlo Results}\label{sec:2}
This section presents Monte Carlo experiments demonstrating that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they study, but can
have substantially higher power when the \dgp\ has a structural
break.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS}
  \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
  dbframe \citep[version 0.2.7]{Cal:10b} packages.}

@@

For comparison, we study this paper's new statistic as well as \poscw\
rolling-window and recursive-window test statistics.  Clark and West
only prove that their rolling-window statistic is asymptotically
normal, and only then if the benchmark model is not estimated, but
their recursive-window statistic is popular in practice and in
simulations tends to perform similarly to their rolling window test.
We use all three of these statistics to test the null that the
benchmark model's innovation is an \mds.\footnote{\citet{ClW:07}
  report the performance of the tests proposed by \citet{CCS:01} and
  \citet{ClM:05} as well, and of tests based on the naive Gaussian
  statistic.}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.\footnote{This statistical analysis was
  conducted in R \citep{R} using the xtable
  \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
  0.2.7]{Cal:10b} packages.}

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-\bootsize\% critical value (1.28)
and the critical value estimated by the procedure of
Theorem~\ref{res:2} (\empiricalcriticalvalue).\footnote{The bootstrap
  uses \nboot\ replications with i.i.d. sampling, as proposed in
  conclusion~\ref{it:1} of Theorem~\ref{res:2}.}  Three predictors are
significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio.  But none are significant after accounting for
data snooping, which highlights the importance of these methods.  The
median forecast is significant using conventional critical values as
well, but not the corrected values.

>>>>

\section{Introduction} This paper proposes an out-of-sample (\oos)
test statistic that is asymptotically normal with mean zero even when
the models studied are nested.
\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.%
\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} %
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %

@@

\section{Monte Carlo Results}\label{sec:2}
This section presents Monte Carlo experiments demonstrating that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they study, but can
have substantially higher power when the \dgp\ has a structural
break.%
\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS}
  \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
  dbframe \citep[version 0.2.7]{Cal:10b} packages.} %

@@

For comparison, we study this paper's new statistic as well as \poscw\
rolling-window and recursive-window test statistics.  Clark and West
only prove that their rolling-window statistic is asymptotically
normal, and only then if the benchmark model is not estimated, but
their recursive-window statistic is popular in practice and in
simulations tends to perform similarly to their rolling window test.
We use all three of these statistics to test the null that the
benchmark model's innovation is an \mds.%
\footnote{\citet{ClW:07}
  report the performance of the tests proposed by \citet{CCS:01} and
  \citet{ClM:05} as well, and of tests based on the naive Gaussian
  statistic.} %

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was
  conducted in R \citep{R} using the xtable
  \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
  0.2.7]{Cal:10b} packages.} %

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-\bootsize\% critical value (1.28)
and the critical value estimated by the procedure of
Theorem~\ref{res:2} (\empiricalcriticalvalue).%
\footnote{The bootstrap
  uses \nboot\ replications with i.i.d. sampling, as proposed in
  conclusion~\ref{it:1} of Theorem~\ref{res:2}.} %
Three predictors are
significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio.  But none are significant after accounting for
data snooping, which highlights the importance of these methods.  The
median forecast is significant using conventional critical values as
well, but not the corrected values.
